---
title: "Join Data with dplyr"
---

```{r setup}
library(tidyverse)
library(nycflights13)

band <- tribble(
   ~name,     ~band,
  "Mick",  "Stones",
  "John", "Beatles",
  "Paul", "Beatles"
)

instrument <- tribble(
    ~name,   ~plays,
   "John", "guitar",
   "Paul",   "bass",
  "Keith", "guitar"
)

instrument2 <- tribble(
    ~artist,   ~plays,
   "John", "guitar",
   "Paul",   "bass",
  "Keith", "guitar"
)
```

# nycflights13

```{r}
View(flights)
```

```{r}
View(airlines)
```

# mutating joins

```{r}
band %>% left_join(instrument, by = "name")
band %>% right_join(instrument, by = "name")
band %>% full_join(instrument, by = "name")
band %>% inner_join(instrument, by = "name")
```


## Your Turn 1

Which airlines had the largest arrival delays? Complete the code below.

1. Join `airlines` to `flights`
2. Compute and order the average arrival delays by airline. Display full names, no codes.

*(Hint: Be sure to remove each `_` before running the code)*

```{r}
flights %>%
  filter(!is.na(arr_delay)) %>%
  __________________  %>%
  group_by(_________) %>%
  __________________  %>%
  arrange(__________) 
```


## Your Turn 2

Join `flights` and `airports`. 

Then for each `name`, compute the `distance` from NYC and the average `arr_delay`.  *Hint: use `first()` to get the first value of distance.*

Order by average delay, worst to best.

*(Hint: Be sure to remove each `_` before running the code)*

```{r}
flights %>% 
  filter(!is.na(arr_delay)) %>%
  ______(airports, __________________) %>%
  group_by(name) %>%
  _________(distance = _____________, 
               delay = _____________) %>%
  ______(_____(delay))
```


# Take aways

* `left_join()` retains all cases in _left_ data set
* `right_join()` retains all cases in _right_ data set
* `full_join()` retains all cases in _either_ data set
* `inner_join()` retains _only_ cases in _both_ data sets


