---
title: "Introduction into R markdown"
author: "Vendula"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 15,
	fig.width = 14,
	message =TRUE,
	warning = TRUE,
	comment = "",
	results = "asis",
	supressMessage = FALSE
	)

library(tidyverse)

```

## Creating an R Markdown file


Each R markddown file contains three types of text:

* An (optional) YAML header surrounded by ---s
* R code chunks surrounded by ```s
* text mixed with simple text formatting

###YAML header

* title: "...."
* author: "...."
* date: "...."
* output: html_document/pdf_document/word_document

     
###Plain text

formating is done using marks  
# Header  
## Header 2  

**bold** with double-asterisks  
_italics_ with underscores  
`code-type` font with backticks  


###Chunk options

write in the bracketes after letter "r" or as general statment e.g. knitr::opts_chunk$set(echo = TRUE) on the beginning

* include = FALSE prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.
* echo = FALSE prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.
* message = FALSE prevents messages that are generated by code from appearing in the finished file.
* warning = FALSE prevents warnings that are generated by code from appearing in the finished.
* fig.cap = "..." adds a caption to graphical results.
* fig.height, fig.width
* results = "markpup" or "asis" or "hide" or "hold"

### Inside chunk
Sometimes is good to have formated text also inside the chunks e.g. when you create the figures or data analysis by loop

* `cat` start for header
* `knitr::kable()` formated table

## Printing the table

```{r table}
df <- iris
df[1,1]<-NA
Head<-head(df)
print(knitr::kable(Head))
```

## Plotting the data and save them

```{r }


for (i in 1:4){
  df$var<-df[,i]
  p<-ggplot(data = df, aes(x=Species, y=var))+geom_boxplot()
print(p)
ggsave(paste(colnames(df)[i],".jpg"))
}

```


## Tasks

1. Write a sentence containing words with bold, italics, and underlined formatting.
1. Create a  plot generated with 3 inches wide and 5 inches high 
1. test different Chunk options for final document